Title

### 2023-06-11 main.tex
Cambios

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}
\usepackage{subcaption}

@@

% array package and thick rules for tables
\usepackage{array}

@@

\newcommand{\fref}[1]{Fig.~\ref{#1}}
\newcommand{\eref}[1]{eq.~(\ref{#1})}
% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

@@

As in the one qubit case, Pauli channels for $N$ qubits 
attenuate the components $r_{\vec{\alpha}}$ of the density matrix.
This can be seen by substituting \eref{eq:  Density matrix Nqbit} in \eref{eq: pauli channel N-qubit}
and using the property of \eref{eq: propiedad-pauli}:
\begin{align*}
\mathcal{E}(\rho) &= \dfrac{1}{2^N} \sum_{\vec{\gamma},\vec{\alpha}} k_{\vec{\gamma}} r_{\vec{\alpha}} \sigma_{\vec{\gamma}} \sigma_{\vec{\alpha}} \sigma_{\vec{\gamma}} \\
& = \dfrac{1}{2^N} \sum_{\vec{\alpha}} \left( \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} \; k_{\vec{\gamma}} \right) r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
\end{align*}
which means that applying the Pauli channel multiplies the 
components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
% }}}
\subsection{Pauli Dynamical Maps} % {{{
\label{subsec: Pauli Dynamical Maps}

@@

\begin{figure} % {{{
\centering
% \begin{quantikz}
% \lstick{$q:\; |0\rangle^{\otimes N}$} & \qw & \gate{\sigma_{\vec{\gamma} }} \gategroup[wires=2,steps
% =1,style={dashed, inner sep=4pt}]{Repeat for all $\vec{\gamma}$}
% \gategroup[wires=2,steps
% =1,style={dashed, inner sep=4pt}, label style = {label position = below, yshift = 0.15cm}]
% {$|\vec{\gamma}\rangle$} & \qw \\
% \lstick{$\tilde{q}:\; |0\rangle^{\otimes 2N}$} & \gate[wires=1]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \ctrl{-1} 
% % \gategroup[wires=1,steps
% %=1,style={color=white, inner sep=0pt}, label style= {label position=below}]{$|\vec{\gamma}\rangle$} 
% & \qw 
% \end{quantikz}
\includegraphics{images/circuito_general.pdf}
\caption{{\bf Circuit for an $N$-qubit
Pauli channel on $N$ qubits.}
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on the $2N$ ancilla qubits denoted by $\tilde{q}$. }
\label{fig: circuit-pauli}
\end{figure} % }}}

The first part of the circuit involves the creation of the state
\begin{eqnarray}
\label{eq: state}
\text{Ancilla state =} 
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$ and
the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined as $|\gamma_1\rangle
\cdots |\gamma_N\rangle$.
When measured in the computational basis, the state given in \eref{eq: state}
collapses to $|\vec{\gamma}\rangle$ with a 
probability $|b_{\vec{\gamma}}|^2 = k_{\vec\gamma}$. 
The circuit in \fref{fig: circuit-pauli} uses this fact
to apply $\sigma_{\vec{\gamma}}$ on the main qubits
with a probability $k_{\vec\gamma}$ by using controlled operations 
conditioned on the state of the system being $|\vec{\gamma}\rangle$,
just as the Pauli channel is supposed to do.  
% 
% that apply $\sigma_{\vec{\gamma}}$ to the main qubits
% only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
% 
% Therefore, the circuit from \fref{fig: circuit-pauli} 
% applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
% with a probability $k_{\vec{\gamma}}$, 
% just as a Pauli channel is supposed to do.

@@

Moreover, it is possible to construct a 1PR circuit to generate any given curve of 
states described by \eref{eq:curve-states}. 
One approach to achieve this is by utilizing the circuit 
depicted in \fref{fig:1PR-circuit}, 
with the parametrized rotation $R$ applied to the last qubit controlled by all the 
other qubits. The operators $A$ and $B$ can be defined as follows:
\begin{align*}
&B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N}-1 \rangle + \sqrt{\langle b | b \rangle} |2^{N}-2\rangle + \sqrt{\langle c |c \rangle} |2^N-3\rangle, \\
&A|2^N-1 \rangle = \frac{1}{\sqrt{\langle a | a \rangle}} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{\sqrt{\langle b | b \rangle}}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{\sqrt{\langle c | c \rangle}}|c\rangle.
\end{align*}
The remaining part of the operators $A$ and $B$ can be defined
in any arbitrary manner as long as they are unitary.
By starting from the initial state $|0\rangle$ and 
applying the circuit shown in \fref{fig:1PR-circuit}, straightforward calculations 
lead us to obtain the resulting curve of states described in Equation (\ref{eq:curve-states}).

@@

\begin{itemize}
\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
$|\beta_0(p)|^2= (1-3p/4)$, $|\beta_1(p)|^2 = |\beta_2(p)|^2 = |\beta_3(p)|^2 = p/4$.
Then, taking the $\beta_j$ to be real,
thi curve of states is
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |00\rangle + \sqrt{p/4} |01\rangle + \sqrt{p/4} |10 \rangle  + \sqrt{p/4} |11\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
\end{align*}
with $\sin s = \sqrt{3p/4}$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.
\cpnote{De nuevo, quizá aca convenga tener notacion de qubits y no de sistemas de 4 niveles}
\tbnote{Va, listo.}

\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} (1-p)^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
the curve of states needed on the ancilla qubits is:
\begin{eqnarray}
|\beta(p)\rangle = \dfrac{1}{2} (1-p) |00\rangle + \dfrac{1}{2} \sqrt{1-p^2} |01\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |10\rangle +  \dfrac{1}{2}(1+p) |11\rangle.
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|00\rangle + \dfrac{1}{2} |11\rangle \right) + e^{is} \left( \dfrac{i}{4}|00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle - \dfrac{i}{4} |11\rangle \right) \\
& + e^{-is}  \left( \dfrac{-i}{4} |00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle + \dfrac{i}{4} |11\rangle \right),
\end{align*}
with $\sin s = p$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle, |b\rangle, |c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|, |b|, |c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle,$ $|c'\rangle = |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$ \cpnote{Esta supongo qeu 
la escoges aleatoriamente, y que la tomas por ahi del CUE. Lo platicamos y metemos 
los detalles. }
and use it to define the states $|a\rangle = V |a'\rangle, |b\rangle = V |b'\rangle, |c\rangle = V |c'\rangle$.
This way, given that the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}.

@@

To fulfill this additional condition,  we restrict the first row of
$V$ written as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
\end{align*}
The last equality comes from the fact
that the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
is obtained by calculating the dot product of the first row of $V$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.}
\end{itemize}

@@

\cpnote{Esta parte está desordenada. Porque parece qeu das el procedimiento 
en los 3 putnos de arriba y leugo que siempre no, qu evalta algo. Trata de iterar el paso 3 
estos dos parrafos para que tengan un flujo mas chido. }
\tbnote{Va, lo cambié y agregué esto al paso 3. Propongo quitar lo rojo y dejar lo morado}
To fulfill this additional condition,  we restrict the first row of
$V$ writen as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
\end{align*}
The last step is because the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
is obtained by calculating the dot product of the first row of $V$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.
}

>>>>

% textcomp cpackage and marvosym package for additional characters
\usepackage{textcomp,marvosym}
\usepackage{subcaption}

@@

% array package and thick rules for tables
\usepackage{array}
\usepackage{caption}
\captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period,name={Fig}}

@@

\newcommand{\fref}[1]{Fig~\ref{#1}}
\newcommand{\eref}[1]{Eq~(\ref{#1})}
% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

@@

As in the one qubit case, Pauli channels for $N$ qubits 
attenuate the components $r_{\vec{\alpha}}$ of the density matrix.
This can be seen by substituting \eref{eq:  Density matrix Nqbit} in \eref{eq: pauli channel N-qubit}
and using the property of \eref{eq: propiedad-pauli}:
\begin{align*}
\mathcal{E}(\rho) &= \dfrac{1}{2^N} \sum_{\vec{\gamma},\vec{\alpha}} k_{\vec{\gamma}} r_{\vec{\alpha}} \sigma_{\vec{\gamma}} \sigma_{\vec{\alpha}} \sigma_{\vec{\gamma}} \\
& = \dfrac{1}{2^N} \sum_{\vec{\alpha}} \left( \sum_{\vec{\gamma}} {(A^{\otimes^N})}_{\vec{\alpha},\vec{\gamma}} \; k_{\vec{\gamma}} \right) r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
\end{align*}
which means that applying the Pauli channel multiplies the 
components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} {(A^{\otimes^N})}_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
% }}}
\subsection{Pauli Dynamical Maps} % {{{
\label{subsec: Pauli Dynamical Maps}

@@

\begin{figure} % {{{
\centering
\includegraphics{images/circuito_general.pdf}
\caption{{\bf Circuit for an $N$-qubit
Pauli channel on $N$ qubits.}
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on the $2N$ ancilla qubits denoted by $\tilde{q}$. }
\label{fig: circuit-pauli}
\end{figure} % }}}

The first part of the circuit involves the creation of the state
\begin{eqnarray}
\label{eq: state}
\text{Ancilla state =} 
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
{|b_{\vec{\gamma}}|}^2 = k_{\vec{\gamma}}$ and
the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined as $|\gamma_1\rangle
\cdots |\gamma_N\rangle$.
When measured in the computational basis, the state given in \eref{eq: state}
collapses to $|\vec{\gamma}\rangle$ with a 
probability ${|b_{\vec{\gamma}}|}^2 = k_{\vec\gamma}$. 
The circuit in \fref{fig: circuit-pauli} uses this fact
to apply $\sigma_{\vec{\gamma}}$ on the main qubits
with a probability $k_{\vec\gamma}$ by using controlled operations 
conditioned on the state of the system being $|\vec{\gamma}\rangle$,
just as the Pauli channel is supposed to do.  
% 
% that apply $\sigma_{\vec{\gamma}}$ to the main qubits
% only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
% 
% Therefore, the circuit from \fref{fig: circuit-pauli} 
% applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
% with a probability $k_{\vec{\gamma}}$, 
% just as a Pauli channel is supposed to do.

@@

Moreover, it is possible to construct a 1PR circuit to generate any given curve of 
states described by \eref{eq:curve-states}. 
One approach to achieve this is by utilizing the circuit 
depicted in \fref{fig:1PR-circuit}, 
with the parametrized rotation $R$ applied to the last qubit controlled by all the 
other qubits. The operators $A$ and $B$ can be defined as follows:
\begin{align*}
&B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N}-1 \rangle + \sqrt{\langle b | b \rangle} |2^{N}-2\rangle + \sqrt{\langle c |c \rangle} |2^N-3\rangle, \\
&A|2^N-1 \rangle = \frac{1}{\sqrt{\langle a | a \rangle}} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{\sqrt{\langle b | b \rangle}}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{\sqrt{\langle c | c \rangle}}|c\rangle.
\end{align*}
The remaining part of the operators $A$ and $B$ can be defined
in any arbitrary manner as long as they are unitary.
By starting from the initial state $|0\rangle$ and 
applying the circuit shown in \fref{fig:1PR-circuit}, straightforward calculations 
lead us to obtain the resulting curve of states described in \eref{eq:curve-states}.

@@

\begin{itemize}
\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 = {|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.
Then, taking the $\beta_j$ to be real,
thi curve of states is
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |00\rangle + \sqrt{p/4} |01\rangle + \sqrt{p/4} |10 \rangle  + \sqrt{p/4} |11\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
\end{align*}
with $\sin s = \sqrt{3p/4}$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.
\cpnote{De nuevo, quizá aca convenga tener notacion de qubits y no de sistemas de 4 niveles}
\tbnote{Va, listo.}

\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} {(1-p)}^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} {(1+p)}^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
the curve of states needed on the ancilla qubits is:
\begin{eqnarray}
|\beta(p)\rangle = \dfrac{1}{2} (1-p) |00\rangle + \dfrac{1}{2} \sqrt{1-p^2} |01\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |10\rangle +  \dfrac{1}{2}(1+p) |11\rangle.
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|00\rangle + \dfrac{1}{2} |11\rangle \right) + e^{is} \left( \dfrac{i}{4}|00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle - \dfrac{i}{4} |11\rangle \right) \\
& + e^{-is}  \left( \dfrac{-i}{4} |00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle + \dfrac{i}{4} |11\rangle \right),
\end{align*}
with $\sin s = p$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$ \cpnote{Esta supongo qeu 
la escoges aleatoriamente, y que la tomas por ahi del CUE. Lo platicamos y metemos 
los detalles. }
and use it to define the states $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$.
This way, given that the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}.

@@

To fulfill this additional condition,  we restrict the first row of
$V$ written as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
\end{align*}
The last equality comes from the fact
that the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.}
\end{itemize}

@@

\cpnote{Esta parte está desordenada. Porque parece qeu das el procedimiento 
en los 3 putnos de arriba y leugo que siempre no, qu evalta algo. Trata de iterar el paso 3 
estos dos parrafos para que tengan un flujo mas chido. }
\tbnote{Va, lo cambié y agregué esto al paso 3. Propongo quitar lo rojo y dejar lo morado}
To fulfill this additional condition,  we restrict the first row of
$V$ writen as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
\end{align*}
The last step is because the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.
}
